Detecting threats of violence in YouTube comments

### 2016-03-03 submission.tex
Shortened previous work section

\newcite{dinakar2011} proposes a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. They adopt a two-stage approach, where the
first stage consists of using a lexicon of negative words and a list
of profane words, as well as part-of-speech tags from the training
data that were correlated with bullying. The second stage is
category-specific, and makes use of commonly observed uni- and bigrams
from each category as features. The experiments reported accuracies
from 63~\% to 80~\%, but did not report precision or recall.
% lists of negative and profane words
% correlated words from training data

There has been quite a bit of work focused on the detection of threats
in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}.
The data set used for these experiments consists of a collection of 5000
threatening tweets collected by a website over a period of about two
years. In addition, a large number of random tweets were collected for
development and testing. A set of 2.3 million random tweets was used
for development, and a set of 1 million was used for testing. 
The system relies on manually constructed recognition patterns, in the
form of n-grams (uni-, bi- and trigrams, as well as skip bi- and
trigrams), but do not go into detail about the methods used to
construct these patterns, stating that the researchers relied on their
(linguistic) intuition as speakers of Dutch \cite{nellngram2013}. In
\newcite{nellshallow2013}, a manually crafted shallow parser is added
to the system. This improves results to a precision of 39\% and a
recall of 59\% \footnote{Perhaps a footnote on the peculiarities of the evaluation??}.
% handcrafted patterns
% rule-based shallow parser
% dubious evaluation

\newcite{warner2012} present a method for detecting unwanted or
illegal comments in user-generated web text from the internet, which
relies on machine learning in combination with template-based
features. The data set used in the research came from two sources. The
first consists of posts from Yahoo news groups, the second were
webpages collected by the American Jewish Congress that had been
identified as offensive. The data set was manually annotated, and then
the hate speech was assigned to a category, such as anti-Semitic,
anti-woman, anti-Asian, etc. The task is then approached as a
word-sense disambiguation task, since the same words can be used in
both hateful and non-hateful contexts. The features used in the
classification were combinations of uni-, bi- and trigrams,
part-of-speech-tags and Brown clusters.  The best results of the
classifications were obtained using only unigrams as features, with a
precision of 67~\% and a recall of 60~\%. The other feature sets
garnered much lower results, and the authors suggest that deeper
parsing could reveal significant phrase patterns.
% only unigrams best results
% suggests parsing might help

\newcite{hammer2014} reports an experiment on the data set that we
will be using in our own experiments, although it has been changed
slightly since the publication of his initial study. The method used a
logistic LASSO regression analysis on bigrams (skip-grams) of
important words to classify sentences as \tovs{} or not.
The method described in the article uses a set of important words that
are correlated with threats of violence. The features are bigrams of
two of these important words observed in the same sentence. The
article does not describe exactly how these important words were
selected, stating only that words were chosen that were significantly
correlated with the response (violent/non-violent sentence). Results are reported only in terms of proportion of false positives for the two classes and it is not clear how the data was split for training and evaluation.

>>>>

\newcite{dinakar2011} propose a method for the detection of
cyberbullying by targeting combinations of profane or negative words,
and words related to several predetermined sensitive topics. Their
data set consists of over 50,000 YouTube comments taken from videos
about controversial topics. %% They adopt a two-stage approach, where the
%% first stage consists of using a lexicon of negative words and a list
%% of profane words, as well as part-of-speech tags from the training
%% data that were correlated with bullying. The second stage is
%% category-specific, and makes use of commonly observed uni- and bigrams
%% from each category as features.
The experiments reported accuracies from 63~\% to 80~\%, but did not
report precision or recall.
% lists of negative and profane words
% correlated words from training data

There has been quite a bit of work focused on the detection of threats
in a data set of Dutch tweets \cite{nellngram2013,nellshallow2013}, which consists of a collection of 5000
threatening tweets collected by a website. In addition, a large number of random tweets were collected for
development and testing. %% A set of 2.3 million random tweets was used
%% for development, and a set of 1 million was used for testing.
The system relies on manually constructed recognition patterns, in the
form of n-grams 
%(uni-, bi- and trigrams, as well as skip bi- and trigrams)
, but do not go into detail about the methods used to
construct these patterns%% , stating that the researchers relied on their
%% (linguistic) intuition as speakers of Dutch \cite{nellngram2013}
. In
\newcite{nellshallow2013}, a manually crafted shallow parser is added
to the system. This improves results to a precision of 39\% and a
recall of 59\%.
% handcrafted patterns
% rule-based shallow parser
% dubious evaluation

\newcite{warner2012} present a method for detecting hate speech in
user-generated web text from the internet, which relies on machine
learning in combination with template-based features. The task
is approached as a word-sense disambiguation task, since the same
words can be used in both hateful and non-hateful contexts. The
features used in the classification were combinations of uni-, bi- and
trigrams, part-of-speech-tags and Brown clusters.  The best results of
the classifications were obtained using only unigrams as features,
with a precision of 67~\% and a recall of 60~\%. The other feature
sets garnered much lower results, and the authors suggest that deeper
parsing could reveal significant phrase patterns.
% only unigrams best results
% suggests parsing might help

Perhaps closest to the current work is the work of
\newcite{hammer2014}, who reports on an experiment on the same data set that
we will be using in our own experiments. The method uses a logistic
LASSO regression analysis on bigrams (skip-grams) of important words
to classify sentences as \tovs{} or not.  The system makes use of a
list of words that are correlated with threats of violence. The
article does not, however, describe exactly how these important words
were selected, stating only that words were chosen that were
significantly correlated with the response (violent/non-violent
sentence). Results are reported only in terms of proportion of false
positives for the two classes and it is not clear how the data was
split for training and evaluation, which makes it difficult to compare with their results.
